Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-02-04 paper/ms.tex
3 paragraphs on the Results section

\section{Introduction}
Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a central topic in studies of structure formation in the Universe. The reason is the diverse range of fields where they are helpful, LAEs can be used as probes of reionization, tracers of large scale structure, signposts for low metallicity stellar populations and markers of the the galaxy formation process through cosmic history.

@@

The model that populates halos with LAEs is based one-to-one correspondence: each halo can only host a single LAE. There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE. In what follows we will describe by the letter ${\mathcal M}$ a model defined by these three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.

@@

The advantage of these three ways of sampling is that it allows us to explore the effects of both cosmic variance and the correlation between fields. Comparing the results of the first and second method will help us to quantify the effect of field correlation, while compating the first and the third method will serve us to gauge the impace of cosmic variance.

@@

We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$. In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 290000$.

@@

@@

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}

>>>>

\section{Introduction}

Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
central topic in studies of structure formation in the Universe. The reason is the diverse range of fields where they are helpful, LAEs can be used as probes of reionization, tracers of large scale structure, signposts for low metallicity stellar populations and markers of the the galaxy formation process through cosmic history.

@@

The model that populates halos with LAEs is based on a one-to-one correspondence: each halo can only host a single LAE. There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE. In what follows we will describe by the letter ${\mathcal M}$ a model defined by these three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.

@@

The advantage of these three sampling ways is that they allow us to explore the effects of both cosmic variance and the correlation between fields. Comparing the results of the first and second method will help us to quantify the effect of field correlation, while compating the first and the third method will serve us to gauge the impace of cosmic variance.

@@

We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$. In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 9\times 10^{4}$.

@@

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with $P>0.1$\label{figure:landscape}.}
\end{figure}

@@

These results distinguish three mass regimes. In the first regime, at high mass values, we find that LAE models with minimum mass of $M_{\rm min}>XXX$ are not compatible with observations as expected from the analysis in the previous subsection. Below this mass down to $M_{\rm min}=XXX$ any minium and maximum mass models are compatible with LAEs observations. In a thirds mass regime, for low mass values $M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is able to reproduce observations.

In these three different mass regimes the occupation monotonically decreases as a function of the minimum halo mass $M_{\rm min}$. In Figure XXX we show this treend in three panels following the same correspondence as Figure XXX. From these results we interpret that the different mass regimes that were identified correspond to best fit models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm occ}\sim 0$, respectively.

There are some models where the KS test yield values of $P\sim 1$. To illustrate the kind of success represented by these models, we have selected these best ones in the case of the method {\tt{MatchObs}}. Figure XXX shows in the main panel the spatial distribution of the mock surveys, the smaller panel shows the corresponding surface density distribution and the observational constraint.
